---
title: "Clean Auction Data"
author: "Jeffrey B. Arnold"
date: "05/22/2015"
output: html_document
---

```{r}
library("dplyr")
library("jsonlite")
library("readr")

fill_na <- function(x, fill = 0) {
  x[is.na(x)] <- fill
  x
}
```

```{r}
source("../../sources/scripts/R/finance.R")
bond_metadata <-
    fromJSON("../bond_metadata.json",
             simplifyDataFrame = FALSE)

make_auction_yields <- 
    function(prices, bond, date)
{
    metadata <- bond_metadata[[as.character(bond)]]
    issue_date <- metadata[["issue_date"]]
    if (! is.na(issue_date) && ! is.null(issue_date)) {
        issue_date <- as.Date(issue_date, format = "%Y-%m-%d")
    } else {
        issue_date <- NULL
    }
    cashflows <-
        mutate(plyr::ldply(metadata[["cashflows"]],
                           function(x) as.data.frame(x)),
               date = as.Date(date, format="%Y-%m-%d"))
    sapply(prices, function(price) {
      as.numeric(yield_to_maturity2(price, date, cashflows))
    })   
}

```


# June 15, 1864 Auction

Average value of the greenback between 1864-06-04, when the auction opened for bids,
and 1864-06-15, when it closed.
```{r eval = FALSE}
read_csv("../greenbacks.csv") %>%
  filter(date >= as.Date("1864-06-04") & date <= as.Date("1864-06-15")) %>%
  na.omit() %>%
  summarize(value = mean(mean))
```
In gold dollars per greenback dollars:
```{r}
GREENBACK_PRICE <- 51.1765 / 100
```
Bids > 4 percent premium were accepted
```{r}
ACCEPT_PREMIUM <- 4
```


```{r}
clean_sixes_1864 <- function(file, auction_name) {
  cleanerdata <- read_csv(file) %>%
    rename(name = bidder) %>%
    mutate(price = bid * GREENBACK_PRICE,
           accepted = amount * (bid > (100 + ACCEPT_PREMIUM)))
  
  metadata <- data.frame(name = auction_name,
                         announcement = as.Date("1864-06-04"),
                         close = as.Date("1864-06-15"),
                         description = "Sixes of 1881")
    
  bidders <- cleanerdata %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = auction_name)

  bids <- cleanerdata %>%
    left_join(bidders %>% select(- price_mean)) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount),
              accepted = sum(accepted)) %>%
    mutate(auction = auction_name,
           coupon_yield = 6 / price,
           yield = make_auction_yields(price, "us_6pct_1881_jul",
                                       as.Date("1864-06-15")))
  list(bidders = bidders, bids = bids,
       metadata = metadata)
}
auction_1864 <-
  clean_sixes_1864("sixes_of_1881_1864-06-04.csv", "1864-06-15; Sixes of 1881")

```


# November 10, 1862 Auction

Average value of the greenback between 1862-11-10, when the auction opened for bids,
and 1864-11-17, when it closed.
```{r eval = FALSE}
read_csv("../greenbacks.csv") %>% filter(date >= as.Date("1862-11-10") & date <= as.Date("1862-11-17")) %>% na.omit() %>% summarize(value = mean(mean))
```
In gold dollars per greenback dollars:
```{r}
GREENBACK_PRICE <- 75.79099 / 100
```

```{r}
auction_18621110_meta <- 
  data_frame(name = "1862-11-10; Seven-Thirties of 1861",
             announcement = as.Date("1862-11-10"),
             close = as.Date("1862-11-17"),
             description = "Seven-Thirties of 1861")

auction_18621110 <- read_csv("1862-11-10_Treasury_Report.csv") %>%
    mutate(accepted = fill_na(accepted),
           price = (bid + 100) * GREENBACK_PRICE)
    
bidders_18621110  <- auction_18621110 %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = "1862-11-10; Seven-Thirties of 1861")

bids_18621110  <- auction_18621110 %>%
    left_join(bidders_18621110 %>% select(- price_mean)) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1862-11-10; Seven-Thirties",
           coupon_yield = 7.3 / price,
           yield = pmin(make_auction_yields(price, "us_seven_thirties_1864_oct_option", as.Date("1862-11-17")),
                        make_auction_yields(price, "us_seven_thirties_1864_oct", as.Date("1862-11-17"))))
           

```

# April 6, 1861 Auction

Notice of auction is on April 6, 1861. Bids accepted until April 11, 1861.

```{r}
auction_18610406_meta <- 
  data_frame(name = "1861-04-06; Treasury Notes of 1861",
             announcement = as.Date("1861-04-06"),
             close = as.Date("1861-04-11"),
             description = "Treasury Notes of 1861 (Two-year)")

auction_18610406 <- read_csv("treasury_notes_of_1861.csv") %>%
    rename(name = bidder, price = value) %>%
    mutate(accepted = fill_na(accepted))
    
bidders_18610406  <- auction_18610406 %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = "1861-04-06; Treasury Notes of 1861")

bids_18610406  <- auction_18610406 %>%
    left_join(bidders_18610406 %>% select(- price_mean)) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    mutate(auction = "1861-04-06; Treasury Notes of 1861",
           coupon_yield = 6 / price,
           yield = make_auction_yields(price, "us_treasury_note_1861",
                                       as.Date("1861-04-11"))
           )

```


# Loan of Feb 1861

```{r}
clean_sixes_1861 <- function(file, auction_name, date) {
  cleanerdata <- read_csv(file) %>%
    select(- rejected) %>%
    rename(price = value, name = bidder) %>%
    mutate(accepted = fill_na(accepted))
    
  bidders <- cleanerdata %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = auction_name)

  bids <- cleanerdata %>%
    left_join(bidders %>% select(- price_mean)) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    mutate(auction = auction_name,
           coupon_yield = 6 / price,
           yield = make_auction_yields(price, "us_6pct_1881_jan", date))
  list(bidders = bidders, bids = bids)
}

```

```{r}
auction_18610213 <- clean_sixes_1861("loan_of_february_1860_1861-02-13.csv",
                             "1861-02-13; Loan of Feb 1861",
                             as.Date('1861-02-23'))
auction_18610213_meta <- 
  data_frame(name = "1861-02-23; Loan of February 1861",
             announcement = as.Date("1861-02-13"),
             close = as.Date("1861-02-23"),
             description = "Loan of February, 1861 (Ac5 of February 8, 1861)")

auction_18610322 <- clean_sixes_1861("loan_of_february_1860_1861-03-22.csv",
                              "1861-03-22; Loan of Feb 1861",
                             as.Date('1861-04-02'))

auction_18610322_meta <- 
  data_frame(name = "1861-03-22; Loan of February 1861",
             announcement = as.Date("1861-03-22"),
             close = as.Date("1861-04-02"),
             description = "Loan of February, 1861 (Act of February 8, 1861)")

auction_18610511 <- clean_sixes_1861("loan_of_february_1860_1861-05-11.csv",
                              "1861-05-11; Loan of Feb 1861",
                             as.Date('1861-05-11'))

auction_18610511_meta <- 
  data_frame(name = "1861-05-11; Loan of February 1861",
             announcement = as.Date("1861-05-11"),
             close = as.Date("1861-05-25"),
             description = "Loan of February, 1861 (Act of February 8, 1861)")


```


# Sept 8, 1860 Auction

Proposal on September 8 1860, bids accepted until October 22, 1860.

```{r}
auction_18600908_meta <- 
  data_frame(name = "1860-10-22; Loan of 1860",
             announcement = as.Date("1860-09-08"),
             close = as.Date("1860-10-22"),
             description = "Loan of 1860 (Fives of 1871)")

auction_18600908 <- read_csv("loan_of_1860.csv") %>%
    rename(name = bidder) %>%
    mutate(accepted = fill_na(accepted) * amount,
           price = 100 + premium)
    
bidders_18600908 <- auction_18600908 %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = "1860-09-08; Loan of 1860")

bids_18600908 <- auction_18600908 %>%
    left_join(bidders_18600908 %>% select(- price_mean)) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    mutate(auction = "1860-09-08; Loan of 1860",
           coupon_yield = 5 / price,
           yield = make_auction_yields(price, "us_5pct_1871",
                                       as.Date("1860-10-22")))
           

```

# Auction of April 17, 1848

Proposals invited on April 17, 1848 [Bayley, p. 146](https://books.google.com/books?id=Ce4JAAAAIAAJ&pg=PA146), closed on June 17, 1848.

```{r}
auction_1848_meta <- 
  data_frame(name = "1848-04-17; Loan of 1848",
             announcement = as.Date("1848-04-17"),
             close = as.Date("1848-06-17"),
             description = "Loan of 1848 (Sixes of 1848)")

auction_1848 <- read_csv("loan_of_1848.csv") %>%
    mutate(accepted = fill_na(accepted) * amount,
           price = 100 + fill_na(premium) + fill_na(premium_fraction))
    
bidders_1848 <- auction_1848  %>%
    group_by(name) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name) %>%
    mutate(bidder_num = row_number(), 
           auction = "1848-04-17; Loan of 1848")

bids_1848  <- auction_1848  %>%
    left_join(bidders_1848  %>% select(- price_mean)) %>%
    select( - name) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1848-04-1; Loan of 1848",
           coupon_yield = 6 / price,
           ytm = make_auction_yields(price, "us_6pct_1868_jul", as.Date("1848-6-17")))

```

# Auction of Feb 9, 1847

```{r}
auction_1847_meta <- 
  data_frame(name = "1847-02-09; Loan of 1847",
             announcement = as.Date("1847-02-09"),
             closed = as.Date("1847-04-10"),
             description = "1847-02-09; Loan of 1847")

auction_1847 <- read_csv("loan_of_1847.csv") %>%
    mutate(accepted = fill_na(accepted),
           price = 100 + fill_na(premium))
    
bidders_1847 <- auction_1847  %>%
    group_by(name) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name) %>%
    mutate(bidder_num = row_number(), 
           auction = "1847-02-09; Loan of 1847")

bids_1847 <- auction_1847  %>%
    left_join(bidders_1847  %>% select(- price_mean)) %>%
    select( - name) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1847-02-09; Loan of 1847",
           coupon_yield = 6 / price,
           yield = make_auction_yields(price, "us_6pct_1868_jan", as.Date("1847-4-10")))

```

# Auction of 1843

Proposals invited on April 2, 1843

```{r}
auction_1843_meta <- 
  data_frame(name = "1843-04-02; Loan of 1843",
             announcement = as.Date("1843-04-02"),
             description = "1843-04-02; Loan of 1843")

auction_1843 <- read_csv("loan_of_1843.csv") %>%
    rename(name = bidder) %>%
    mutate(accepted = fill_na(accepted),
           price = 100 + fill_na(premium))
    
bidders_1843 <- auction_1843 %>%
    group_by(name) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name) %>%
    mutate(bidder_num = row_number(), 
           auction = "1843-04-02; Loan of 1843")

bids_1843 <- auction_1843  %>%
    left_join(bidders_1843  %>% select(- price_mean)) %>%
    select( - name) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1843-04-02; Loan of 1843",
           coupon_yield = 5 / price,
           yield = make_auction_yields(price, "us_5pct_1853", as.Date("1843-04-02")))

```


# Combine and Save

```{r}
bidders <-
  bind_rows(auction_18610213$bidders,
            auction_18610322$bidders,
            auction_18610511$bidders,
            auction_1864$bidders,
            bidders_18600908,
            bidders_18610406,
            bidders_18621110,
            bidders_1847,
            bidders_1848,
            bidders_1843)

bids <-
  bind_rows(auction_18610213$bids,
            auction_18610322$bids,
            auction_18610511$bids,
            auction_1864$bids,
            bids_18600908,
            bids_18610406,
            bids_18621110,
            bids_1847,
            bids_1848,
            bids_1843)

metadata <- 
  bind_rows(auction_18610213_meta,
            auction_18610322_meta,
            auction_18610511_meta,
            auction_1864$metadata,
            auction_18600908_meta,
            auction_18610406_meta,
            auction_18621110_meta,
            auction_1847_meta,
            auction_1848_meta,
            auction_1843_meta)

write.csv(bids, file = "bids.csv", na = "", row.names = FALSE)
write.csv(bidders, file = "bidders.csv", na = "", row.names = FALSE)
write.csv(metadata, file = "metadata.csv", na = "", row.names = FALSE)
```


