---
title: "Clean Auction Data"
author: "Jeffrey B. Arnold"
date: "05/22/2015"
output: html_document
---

```{r}
source("../../R/.init.R")
bond_metadata <- get_bond_metadata("../../data/bond_metadata.json")

make_auction_yields <- function(prices, date, gold_rate, metadata)
{

    if (gold_rate == 1) {
      yields1 <- sapply(prices, function(price) {    
        as.numeric(yield_to_maturity2(price, date, metadata$cashflows))
      })
      data_frame(
        ytm1 = yields1,
        ytm2 = yields1,
        ytm3 = yields1,
        ytm4 = yields1,
        ytm5 = yields1,
        ytm6 = yields1)
    } else {
      cashflows <- metadata$cashflows
      data_frame(price = prices) %>%
        rowwise() %>%
        do({
          yields1 <-
            yield_to_maturity2(.$price * gold_rate, date, cashflows)
          # yields using gold current price
          yields2 <-
            gold_cashflows(cashflows, gold_rate) %>%
            yield_to_maturity2(.$price, date, .) %>%
            as.numeric()
          # yields using currency with implied gold redemption
          yields3 <-
            gold_cashflows_redemp(cashflows, date, gold_rate,
                                  r = 0.04) %>%
            yield_to_maturity2(.$price, date, .) %>%
            as.numeric()
          yields4 <-
            gold_cashflows_redemp(cashflows, date, gold_rate,
                                  r = 0.05) %>%
            yield_to_maturity2(.$price, date, .) %>%
            as.numeric()
          # yields using currency with implied gold redemption
          yields5 <-
            gold_cashflows_redemp(cashflows, date, gold_rate,
                                  r = 0.06) %>%
            yield_to_maturity2(.$price, date, .) %>%
            as.numeric()
          yields6 <-
            gold_cashflows_redemp(cashflows, date, gold_rate,
                                  r = yields1) %>%
            yield_to_maturity2(.$price, date, .) %>%
            as.numeric()
          data_frame(
            ytm1 = yields1,
            ytm2 = yields2,
            ytm3 = yields3,
            ytm4 = yields4,
            ytm5 = yields5,
            ytm6 = yields6)
        })
    }
}

```


# June 15, 1864 Auction

Average value of the greenback between 1864-06-04, when the auction opened for bids,
and 1864-06-15, when it closed.
```{r eval = FALSE}
read_csv("../../data/greenbacks.csv") %>%
  filter(date >= as.Date("1864-06-04") & date <= as.Date("1864-06-15")) %>%
  na.omit() %>%
  summarize(value = mean(mean))
```
In gold dollars per greenback dollars:
```{r}
GREENBACK_PRICE <- 51.1765 / 100
```
Bids > 4 percent premium were accepted
```{r}
ACCEPT_PREMIUM <- 4
```


```{r}
auction_name <- "1864-06-15; Sixes of 1881"
auction_1864 <- read_csv("sixes_of_1881_1864-06-04.csv") %>%
    rename(name = bidder) %>%
    mutate(price = bid,
           accepted = amount * (bid > (100 + ACCEPT_PREMIUM)))
  
auction_1864_meta <- data.frame(name = auction_name,
                            announcement = as.Date("1864-06-04"),
                            close = as.Date("1864-06-15"),
                            description = "Sixes of 1881")
    
bidders_1864 <- auction_1864 %>%
  group_by(name, city, state) %>%
  summarize(price_mean =
              weighted.mean(price, amount)) %>% 
  ungroup() %>%
  arrange(-price_mean, name, city, state) %>%
  mutate(bidder_num = row_number(), 
         auction = auction_name)

bids_1864 <- auction_1864 %>%
  left_join(bidders_1864 %>% select(- matches("price_")), 
            by = c("name", "city", "state")) %>%             
  select( - name, - state, - city) %>%
  group_by(bidder_num, price) %>%
  summarize(amount = sum(amount),
            accepted = sum(accepted)) %>%
  ungroup() %>%
  rename(price_currency = price) %>%
  mutate(auction = auction_name,
         price_gold = price_currency * GREENBACK_PRICE,
         current_yield1 = 6 / (price_currency * GREENBACK_PRICE),
         current_yield2 = 6 / price_currency,
         gold_rate = 1 / GREENBACK_PRICE) %>%
  bind_cols(.,
            make_auction_yields(prices = .$price_currency,
                                date = as.Date("1864-06-15"),
                                gold_rate = 1 / GREENBACK_PRICE, 
                                metadata = bond_metadata[["us_6pct_1881_jul"]]))

```


# November 10, 1862 Auction

Average value of the greenback between 1862-11-10, when the auction opened for bids,
and 1864-11-17, when it closed.
```{r eval = FALSE}
read_csv("../../data/greenbacks.csv") %>%
  filter(date >= as.Date("1862-11-10") & date <= as.Date("1862-11-17")) %>%
  na.omit() %>%
  summarize(value = mean(mean))
```
In gold dollars per greenback dollars:
```{r}
GREENBACK_PRICE <- 75.79099 / 100
```


The option to convert into the 6's of 1881 is used since it implied as lower yield in general.

```{r}
auction_18621110_meta <- 
  data_frame(name = "1862-11-10; Seven-Thirties of 1861",
             announcement = as.Date("1862-11-10"),
             close = as.Date("1862-11-17"),
             description = "Seven-Thirties of 1861")

auction_18621110 <- read_csv("1862-11-10_Treasury_Report.csv") %>%
    mutate(accepted = fill_na(accepted),
           price = (bid + 100))
    
bidders_18621110  <- auction_18621110 %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = "1862-11-10; Seven-Thirties of 1861")

bids_18621110  <- auction_18621110 %>%
    left_join(bidders_18621110 %>% select(- price_mean),
              by = c("name", "city", "state")) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1862-11-10; Seven-Thirties",
           current_yield1 = 7.3 / (price * GREENBACK_PRICE),
           current_yield2 = 7.3 / price,
           price_gold = price * GREENBACK_PRICE,
           gold_rate = 1 / GREENBACK_PRICE) %>%
    rename(price_currency = price) %>%
    bind_cols(., make_auction_yields(.$price_currency,
              as.Date("1862-11-17"),
              1 / GREENBACK_PRICE, 
              bond_metadata[["us_seven_thirties_1864_oct_option"]]))

```

# April 6, 1861 Auction

Notice of auction is on April 6, 1861. Bids accepted until April 11, 1861.

```{r}
auction_18610406_meta <- 
  data_frame(name = "1861-04-06; Treasury Notes of 1861",
             announcement = as.Date("1861-04-06"),
             close = as.Date("1861-04-11"),
             description = "Treasury Notes of 1861 (Two-year)")

auction_18610406 <- read_csv("treasury_notes_of_1861.csv") %>%
    rename(name = bidder, price = value) %>%
    mutate(accepted = fill_na(accepted))
    
bidders_18610406  <- auction_18610406 %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = "1861-04-06; Treasury Notes of 1861")

bids_18610406  <- auction_18610406 %>%
    left_join(bidders_18610406 %>% select(- price_mean),
              by = c("name", "city", "state")) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    mutate(auction = "1861-04-06; Treasury Notes of 1861",
           current_yield1 = 6 / price,
           current_yield2 = current_yield1,
           price_gold = price,
           gold_rate = 1) %>%
    rename(price_currency = price) %>%
    bind_cols(., make_auction_yields(.$price_currency,
              as.Date("1861-04-11"),
              1, bond_metadata[["us_treasury_note_1861"]]))

```


# Loan of Feb 1861

```{r}
clean_sixes_1861 <- function(file, auction_name, date, metadata) {
  cleanerdata <- read_csv(file) %>%
    select(- rejected) %>%
    rename(price = value, name = bidder) %>%
    mutate(accepted = fill_na(accepted))
    
  bidders <- cleanerdata %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = auction_name)

  bids <- cleanerdata %>%
    left_join(bidders %>% select(- price_mean),
              by = c("name", "city", "state")) %>%
    select( - name, - state, - city) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    mutate(auction = auction_name,
           current_yield1 = 6 / price,
           current_yield2 = current_yield1,
           price_gold = price,
           gold_rate = 1) %>%
    rename(price_currency = price) %>%
    bind_cols(., 
              yield = make_auction_yields(.$price_currency, date, 1,
                                          bond_metadata[["us_6pct_1881_jan"]]))
  list(bidders = bidders, bids = bids)
}

```

```{r}
auction_18610213 <- clean_sixes_1861("loan_of_february_1860_1861-02-13.csv",
                             "1861-02-13; Loan of Feb 1861",
                             as.Date('1861-02-23'))
auction_18610213_meta <- 
  data_frame(name = "1861-02-23; Loan of February 1861",
             announcement = as.Date("1861-02-13"),
             close = as.Date("1861-02-23"),
             description = "Loan of February, 1861 (Ac5 of February 8, 1861)")

auction_18610322 <- clean_sixes_1861("loan_of_february_1860_1861-03-22.csv",
                              "1861-03-22; Loan of Feb 1861",
                             as.Date('1861-04-02'))

auction_18610322_meta <- 
  data_frame(name = "1861-03-22; Loan of February 1861",
             announcement = as.Date("1861-03-22"),
             close = as.Date("1861-04-02"),
             description = "Loan of February, 1861 (Act of February 8, 1861)")

auction_18610511 <- clean_sixes_1861("loan_of_february_1860_1861-05-11.csv",
                              "1861-05-11; Loan of Feb 1861",
                             as.Date('1861-05-11'))

auction_18610511_meta <- 
  data_frame(name = "1861-05-11; Loan of February 1861",
             announcement = as.Date("1861-05-11"),
             close = as.Date("1861-05-25"),
             description = "Loan of February, 1861 (Act of February 8, 1861)")


```


# Sept 8, 1860 Auction

Proposal on September 8 1860, bids accepted until October 22, 1860.

```{r}
auction_18600908_meta <- 
  data_frame(name = "1860-10-22; Loan of 1860",
             announcement = as.Date("1860-09-08"),
             close = as.Date("1860-10-22"),
             description = "Loan of 1860 (Fives of 1871)")

auction_18600908 <- read_csv("loan_of_1860.csv") %>%
    rename(name = bidder) %>%
    mutate(accepted = fill_na(accepted) * amount,
           price = 100 + premium)
    
bidders_18600908 <- auction_18600908 %>%
    group_by(name, city, state) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name, city, state) %>%
    mutate(bidder_num = row_number(), 
           auction = "1860-09-08; Loan of 1860")

bids_18600908 <- auction_18600908 %>%
  left_join(bidders_18600908 %>% select(- price_mean),
            by = c("name", "city", "state")) %>%
  select( - name, - state, - city) %>%
  group_by(bidder_num, price) %>%
  summarize(amount = sum(amount), accepted = sum(accepted)) %>%
  mutate(auction = "1860-09-08; Loan of 1860",
         current_yield1 = 5 / price,
         current_yield2 = current_yield1,
         gold_rate = 1,
         price_gold = price) %>%
  rename(price_currency = price) %>%
  bind_cols(.,
            make_auction_yields(.$price_currency,
                                as.Date("1860-10-22"),
                                1,
                                bond_metadata[["us_5pct_1871"]]))
           

```

# Auction of April 17, 1848

Proposals invited on April 17, 1848 [Bayley, p. 146](https://books.google.com/books?id=Ce4JAAAAIAAJ&pg=PA146), closed on June 17, 1848.

```{r}
auction_1848_meta <- 
  data_frame(name = "1848-04-17; Loan of 1848",
             announcement = as.Date("1848-04-17"),
             close = as.Date("1848-06-17"),
             description = "Loan of 1848 (Sixes of 1848)")

auction_1848 <- read_csv("loan_of_1848.csv") %>%
    mutate(accepted = fill_na(accepted) * amount,
           price = 100 + fill_na(premium) + fill_na(premium_fraction))
    
bidders_1848 <- auction_1848  %>%
    group_by(name) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name) %>%
    mutate(bidder_num = row_number(), 
           auction = "1848-04-17; Loan of 1848")

bids_1848  <- auction_1848  %>%
    left_join(bidders_1848  %>% select(- price_mean),
              by = "name") %>%
    select( - name) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1848-04-1; Loan of 1848",
           current_yield1 = 6 / price,
           current_yield2 = current_yield1,
           gold_rate = 1,
           price_gold = price) %>%
  rename(price_currency = price) %>%
  bind_cols(., 
            make_auction_yields(.$price_currency, as.Date("1848-6-17"), 1,
                                bond_metadata[["us_6pct_1868_jul"]]))

```

# Auction of Feb 9, 1847

```{r}
auction_1847_meta <- 
  data_frame(name = "1847-02-09; Loan of 1847",
             announcement = as.Date("1847-02-09"),
             closed = as.Date("1847-04-10"),
             description = "1847-02-09; Loan of 1847")

auction_1847 <- read_csv("loan_of_1847.csv") %>%
    mutate(accepted = fill_na(accepted),
           price = 100 + fill_na(premium))
    
bidders_1847 <- auction_1847  %>%
    group_by(name) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name) %>%
    mutate(bidder_num = row_number(), 
           auction = "1847-02-09; Loan of 1847")

bids_1847 <- auction_1847  %>%
    left_join(bidders_1847  %>% select(- price_mean),
              by = "name") %>%
    select( - name) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1847-02-09; Loan of 1847",
           current_yield1 = 6 / price,
           current_yield2 = current_yield1,
           gold_rate = 1,
           price_gold = price) %>%
  rename(price_currency = price) %>%
  bind_cols(.,
            make_auction_yields(.$price_currency, 
                                as.Date("1847-4-10"), 1,
                                bond_metadata[["us_6pct_1868_jan"]]))

```

# Auction of 1843

Proposals invited on April 2, 1843

```{r}
auction_1843_meta <- 
  data_frame(name = "1843-04-02; Loan of 1843",
             announcement = as.Date("1843-04-02"),
             description = "1843-04-02; Loan of 1843")

auction_1843 <- read_csv("loan_of_1843.csv") %>%
    rename(name = bidder) %>%
    mutate(accepted = fill_na(accepted),
           price = 100 + fill_na(premium))
    
bidders_1843 <- auction_1843 %>%
    group_by(name) %>%
    summarize(price_mean = weighted.mean(price, amount)) %>% 
    ungroup() %>%
    arrange(-price_mean, name) %>%
    mutate(bidder_num = row_number(), 
           auction = "1843-04-02; Loan of 1843")

bids_1843 <- auction_1843  %>%
    left_join(bidders_1843  %>% select(- price_mean),
              by = "name") %>%
    select( - name) %>%
    group_by(bidder_num, price) %>%
    summarize(amount = sum(amount), accepted = sum(accepted)) %>%
    arrange(bidder_num, price) %>%
    mutate(auction = "1843-04-02; Loan of 1843",
           current_yield1 = 5 / price,
           current_yield2 = current_yield1,
           gold_rate = 1,
           price_gold = price) %>%
  rename(price_currency = price) %>%
  bind_cols(., 
            make_auction_yields(.$price_currency,
                                as.Date("1843-04-02"), 1,
                                bond_metadata[["us_5pct_1853"]]))

```


# Combine and Save

```{r}
bidders <-
  bind_rows(auction_18610213$bidders,
            auction_18610322$bidders,
            auction_18610511$bidders,
            bidders_1864,
            bidders_18600908,
            bidders_18610406,
            bidders_18621110,
            bidders_1847,
            bidders_1848,
            bidders_1843) %>%
  mutate(institutional = 
          grepl("(\\&|\\b(son|co(mpany)?|bro(thers?)?|insurance|bank|trustees?|savings|institution|others|cashier|president|executor)\\b)",
                name, ignore.case = TRUE, perl = TRUE))
                

bids <-
  bind_rows(auction_18610213$bids,
            auction_18610322$bids,
            auction_18610511$bids,
            bids_1864,
            bids_18600908,
            bids_18610406,
            bids_18621110,
            bids_1847,
            bids_1848,
            bids_1843)

metadata <- 
  bind_rows(auction_18610213_meta,
            auction_18610322_meta,
            auction_18610511_meta,
            auction_1864_meta,
            auction_18600908_meta,
            auction_18610406_meta,
            auction_18621110_meta,
            auction_1847_meta,
            auction_1848_meta,
            auction_1843_meta)

write.csv(bids, file = "bids.csv", na = "", row.names = FALSE)
write.csv(bidders, file = "bidders.csv", na = "", row.names = FALSE)
write.csv(metadata, file = "metadata.csv", na = "", row.names = FALSE)
```


