---
title: "Auctions of the 6’s of 1881"
author: "Jeffrey Arnold"
date: "September 7, 2015"
output: html_document
---

The sixes of 1881 were authorized by an act in February 1861, prior to the American Civil War, to pay for a government budget deficit unrelated to what would be the war.
What makes them interesting is that they were auctioned off over three auctions: Feb 13, Mar 22, and May 11. 
Two of these auctions were before the Battle of Fort Sumter, and one was after.
Thus you can see investors bidding on the same asset just before and just after the start of the war.

```{r}
library("dplyr")
library("ggplot2")

bids <- read.csv("../sources/auctions/bids.csv", stringsAsFactors = FALSE) %>%
  filter(grepl("Loan of Feb 1861", auction))

head(select(bidder_num, price_currency, amount, accepted), bids)

bidders <- read.csv("../sources/auctions/bidders.csv", stringsAsFactors = FALSE) %>%
  filter(grepl("Loan of Feb 1861", auction))

head(bidders)
```

A summary of the bids (one point for each bidder, with their average bid)
```{r}
ggplot(bidders, aes(x = auction, y = price_mean)) +
  geom_boxplot() + 
  coord_flip()
```


